---
title: HLAClustRView
author: Nissim Ranade, Santiago Medina, Adewunmi Adelaja, Astrid Deschenes and Pascal Belleau
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
bibliography: biblio.bibtex
vignette: |
  %\VignetteIndexEntry{TODO}     
  %\VignettePackage{HLAClustRView}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown} 
---

```{r style, echo = FALSE, results = 'asis', warning=FALSE, message=FALSE}
library(knitr)
library(HLAClustRView)
```

<br />

**Package**: `r packageDescription("HLAClustRView")[["Package"]]` <br />
**Authors**: `r packageDescription("HLAClustRView")[["Author"]]` <br />
**Version**: `r packageDescription("HLAClustRView")$Version` <br />
**Compiled date**: `r Sys.Date()` <br />
**License**: `r packageDescription("HLAClustRView")[["License"]]` <br />


# Licensing  #

The *`r packageDescription("HLAClustRView")[["Package"]]`* package and the 
underlying *`r packageDescription("HLAClustRView")[["Package"]]`* code 
are distributed under the MIT license. You are free to use and 
redistribute this software.

# Citing #

If you use the *`r packageDescription("HLAClustRView")[["Package"]]`* package 
for a publication, we would ask you to cite the following:

> Nissim Ranade, Santiago Medina, Adewunmi Adelaja, Astrid Deschênes and Pascal Belleau (2018). HLAClustRView: HLA typing clustering and
  visualization based on specific similarity metrics. R package version 0.99.0.

# Introduction #

TODO

Since 1998, the IMGT/HLA Database [@Abraham2018] has provided curated 
information about polymorphism in the genes of the immune system.

TODO

# Metrics which estimate similarity between two HLA typing #

To enable quantification of the similarity between two HLA typing, similarity
metric must be used.

## Hamming distance based on first typing field ##

TODO

# An analysis step by step #

## 1. Loading the HLAClustRView package

```{r loadingPackage, warning=FALSE, message=FALSE} 
library(HLAClustRView)
```

TODO

# Session info

Here is the output of sessionInfo() on the system on which this document 
was compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```


# References

